Are you moving predictably?

### 2018-07-11 dokumentation/data_findings.tex
Data analysis weiter geschrieben

	In figure \ref{fig:origin_destination_reason} we see the reason (color of dots) why people move from their origin to a destination. It can be seen, that the vast majority of people are working and that there are metropoliton areas inside the city.

\end{minipage}

>>>>

	In figure \ref{fig:origin_destination_reason} we see the reason (color of dots) why people move from their origin to a destination. It can be seen, that the vast majority of people is working and that there are metropoliton areas inside the city. Some areas, for example around 180, tend to be more visited for academic purposes but since no matter what socio-economic strata people belong, they educate themselves i. e. there is not enough correlation between origin, destination and reason to see clusters which resemble the stratification just by plotting the data in this way. As in the original paper stated (TOOD: cite), there are differences between the stratas, which can be seen when plotting the strata as color column. For example plotting the means of transportation and the reason of travel by taking an equally distributed subset of the data set into account, the richest and poorest people have the most remarkable properties, i. e. the population of strata 1 is only working, studying and returning home by using first and second means of transportation, whilst the reasons for movements of people from strata 6 are more spread but mostly using the third means of transportation, which seems to be only affordable for wealthy people.	 
\end{minipage}\\

We observe, that there are visible differences between the different given stratifications. But since the population of each strata is not homogenous and the clear distinction of two succeeding is not given, we can not see clusters by plotting the data without knowing the result. In the following sections we are therefore investigating approaches to find clusters using different clustering algorithms.
